\chapter{Electrical Circuits I}
\section{Resistors}

\subsection{Resistor Notation - Algebraic Definition}

\defn{Resistor}{A resistor is a two-terminal passive electrical component that implements electrical resistance as a circuit element.}

\begin{displaymath}
    \begin{circuitikz}
        \draw (0,0) to[R, l=$R$] (2,0);
    \end{circuitikz}
\end{displaymath}

\defn{Algebraic Definition}{The algebraic definition of a resistor is given by Ohm's Law, which states that the current through a conductor between two points is directly proportional to the voltage across the two points.}

\begin{equation}
    D: v \longrightarrow i \quad \text{where} \quad v = i \cdot R
    V = i \cdot R
\end{equation}

\begin{itemize}
  \item{Resistance as a function of voltage and current}
  \item{Unit \[\frac{V}{A} = \Omega\]}
\end{itemize}

\newpage

\subsection{Resistor Notation - Geometric Definition}
\defn{Geometric Definition}{The geometric definition of a resistor is given by the resistor's physical properties, such as its length, cross-sectional area, and resistivity.}

% resistor diagram
\begin{displaymath}
    \begin{circuitikz}
        \draw (0,0) to[R, l=$R$, a=$\rho$] (2,0);
    \end{circuitikz}
\end{displaymath}

\begin{equation}
  R = \rho \cdot \frac{l}{A}
\end{equation}
where: 
\begin{itemize}
  \item{$R$ is the resistance of the resistor}
  \item{$\rho$ is the resistivity of the material}
  \item{$l$ is the length of the resistor}
  \item{$A$ is the cross-sectional area of the resistor}
\end{itemize}

\newpage
\subsubsection{Geometrical Interpretation of Resistance as Relationship between Voltage and Current}.

Let's consider the following diagram, which represents a resistor with a voltage source connected to it. The voltage source creates an electric field within the resistor, which causes the free electrons to move in the direction of the electric field. This movement of electrons creates a current flow through the resistor.
% graph of resistance and its derivative
\begin{displaymath}
\begin{tikzpicture}
\begin{axis}[
    title={Resistance and voltage derivative of a non-electrical variable},
    xlabel={$v$},
    ylabel={$i$},
    domain=0:2,
    samples=100,
    legend pos=north west
]
\addplot [blue] {x}; % v = i (linear function)
\addlegendentry{$v = i$}

\addplot [red] {1}; % derivative of v = i (constant function)
\addlegendentry{$\frac{dv}{di} = 1$}
\end{axis}
\end{tikzpicture}
\end{displaymath}

\newpage

\section{Circuit Analysis}

\subsection{Kirchhoff's Laws}

\defn{Kirchhoff's Laws}{Kirchhoff's Laws are two fundamental laws that govern the behavior of electrical circuits.}

\emph{There is two things to consider: devices and topology restrictions.}

\begin{itemize}
  \item{Kirchhoff's Current Law (KCL)}
  \item{Kirchhoff's Voltage Law (KVL)}
  \item{Devices: resistors, capacitors, inductors, etc.}
\end{itemize}

\subsubsection{Kirchhoff's Current Law - KCL}

\defn{Kirchhoff's Current Law}{Kirchhoff's Current Law states that the sum of currents entering a node is equal to the sum of currents leaving a node.}

\begin{equation}
  \sum_{i=1}^{n} i_{\text{in}} = \sum_{i=1}^{n} i_{\text{out}}
\end{equation}


\begin{quote}

  The circuit diagrams above illustrate \emph{Kirchhoff's Current Law}(KCL), 
which states that the algebraic sum of currents entering a node (or a junction) equals zero. 
This principle is a consequence of the conservation of electric charge. 

In the first diagram, we see positive charges $(+)$ flowing into a node. Each arrow represents a current path, 
and the label $i_{\text{in}}^-$ indicates that these are incoming currents. In the second diagram, we see negative charges $(-)$ flowing out of a node, 
which represent electrons moving out of the node, creating a current. 

The arrows again indicate the direction of the current flow, and the label $i_{\text{out}}^-$ indicates that these are outgoing currents. According to KCL, 
the sum of the incoming currents should equal the sum of the outgoing currents at a node, which is visually represented in these diagrams.

\end{quote}

The graph below illustrates the concept of Kirchhoff's Current Law, showing the algebraic sum of currents entering a node equal to zero in the passive convention.

\begin{figure}[ht]
  \centering
  \begin{minipage}{.5\textwidth}
    \centering
    \begin{circuitikz}
      \draw (0,0) node[circ] {} -- (2,0) to[short, i=$i_{\text{in}}^-$] (1,0);
      \draw (0,0) -- (-2,0) to[short, i=$i_{\text{in}}^-$] (-1,0);
      \draw (0,0) -- (0,2) to[short, i=$i_{\text{in}}^-$] (0,1);
      \draw (0,0) -- (0,-2) to[short, i=$i_{\text{in}}^-$] (0,-1);
    \end{circuitikz}
    \caption{{Positive charges $(+)$ flowing into the node}}    
  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \centering
    \begin{circuitikz}
      \draw (0,0) node[circ] {} -- (1,0) to[short, i=$i_{\text{out}}^-$] (2,0);
      \draw (0,0) -- (-1,0) to[short, i=$i_{\text{out}}^-$] (-2,0);
      \draw (0,0) -- (0,1) to[short, i=$i_{\text{out}}^-$] (0,2);
      \draw (0,0) -- (0,-1) to[short, i=$i_{\text{out}}^-$] (0,-2);
    \end{circuitikz}
    \caption{{Negative charges $(-)$ flowing out of the node}}
  \end{minipage}
\end{figure}

\newpage

\subsubsection{Kirchhoff's Voltage Law - KVL}

\defn{Kirchhoff's Voltage Law}{Kirchhoff's Voltage Law states that the sum of voltages around a closed loop is equal to zero.}

\emph{At any closed loop, the sum of the voltage sources is equal to the sum of the voltage drops.}

\begin{equation}
  \sum_{i=1}^{n} v_{\text{in}} = \sum_{i=1}^{n} v_{\text{out}}
\end{equation}

\begin{quote}
The circuit diagram above represents a node with negative charges flowing out. This is a visualization of 
Kirchhoff's Current Law, which states that the algebraic sum of currents entering a node (or a junction) equals zero. 
In this case, the negative charges represent electrons moving out of the node, which creates a current. \\

The arrows indicate the direction of the current flow. Each arrow represents a current path, and the label \boldmath{$i_{\text{out}}^-$} 
indicates that these are outgoing currents. This diagram is a useful tool for understanding the behavior of electrical circuits, 
particularly the principle of conservation of electric charge, which is the basis of \emph{Kirchhoff's Current Law.}

\end{quote}

\emph{Sum of voltages around a closed loop is equal to zero independent of the direction of the loop.}
\begin{figure}[ht]
  \centering
  \begin{minipage}{.5\textwidth}
    \centering
    \begin{align}
      V_g &= V_1 + V_2 + V_3 \nonumber \\
      &= i_g \cdot R_1 + i_g \cdot R_2 + i_g \cdot R_3 \nonumber \\
      &= i_g \cdot (R_1 + R_2 + R_3) \nonumber \\
      &= i_g \cdot R_{\text{eq}}
  \end{align}
    \caption{{Circuit from $+$ to $-$}}
  \end{minipage}%
  \begin{minipage}{.5\textwidth}
    \centering
    \begin{align}
      V_g &= - V_1 - V_2 - V_3 \nonumber \\
      &\therefore \  R^{+}_{eq} \equiv R^{-}_{eq} \nonumber \\
  \end{align}
    \caption{{Circuit from $-$ to $+$}}
  \end{minipage}
\end{figure}

% example 1 here

\newpage
\subsubsection{{Example I. Kirchhoff's Laws in a Series Circuit with Resistors}}

\input{/Users/lucashelal/Desktop/eel/glossary/src/str/examples/kirchhof.tex}

\newpage
\subsubsection{Example II. Proof that the direction of the loop does not affect the application of KVL}

\input{/Users/lucashelal/Desktop/eel/glossary/src/str/examples/kirchhof2.tex}